Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-06 text/paper/paper1.tex
discussion section sec com

These two varieties of grammaticalism give rise to different
predictions about preferred readings. The preference for readings that
weak grammaticalism predicts mirrors the entailment relations in
(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
\as-sentences weak grammaticalism predicts that local readings are
preferred over global readings which in turn are preferred over
literal readings; for \es-sentences strong grammaticalism predicts
that global readings are most preferred, while literal and local
readings are not ranked with respect to preference. Strong
grammaticalism, on the other hand, predicts that both \as- and
\es-sentences preferably get either a local or a global reading rather
than a literal reading. But strong grammaticalism does not rank these
former two with respect to each other because they differ in more than
one application of the $\exh(\cdot)$ operator.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lcc}
    & \multicolumn{2}{c}{preference \& availability}
    \\ \cmidrule(r){2-3}
    theoretical position
    & \as
    & \es
    \\ \midrule
    traditionalism
    \\
    \ \ weak restricted 
    & \lit > \glb 
    & \lit > \glb
    \\
    \ \ weak unrestricted
    & \lit > \glb > \loc 
    & \lit > \glb
    \\
    \ \ strong restricted
    & \glb > \lit 
    & \glb > \lit
    \\
    \ \ strong unrestricted
    & \glb > \loc > \lit 
    & \glb > \lit
    \\
    conventionalism
    \\
    \ \ defaultism
    & \loc >  \lit 
    & \loc >  \lit
    \\
    \ \ literalism
    & \lit >  \loc 
    & \lit >  \loc
    \\
    grammaticalism
    \\
    \ \ weak
    & \loc > \glb > \lit 
    & \glb > \lit, \loc
    \\
    \ \ strong
    & \glb, \loc > \lit 
    & \glb, \loc >  \lit
    \\
  \end{tabular}
  \caption{Predictions of the relevant theoretical positions. Listed
    are the predicted preference relations. If a reading is not
    listed, it is predicted to be unavailable.}
  \label{tab:predictions}
\end{table}

@@

High scores of success in our general control condition clearly
indicate that participants understood the incremental verification
task and were in general able to give judgements at the earliest
possible point in a picture sequence. Results obtained for the
preference-related target conditions moreover show that our design is
able to detect multiple readings and preferences on these. Crucially,
the amount of response types for \lc- and \ec-readings reflected the
known preference for the former, irrespective of the order in which
each reading could first be judged in a given sequence. Given this,
the best and most straightforward explanation of the observed response
type frequencies in our target condition is the hypothesis that the
actual preferences among readings for both \as- and \es-sentences
alike are:
\begin{exe}
  \ex \label{bsp:observed-preferences} \lit \ > \ \loc \ \ ( > \glb)
\end{exe}
where it is unclear whether the global readings are entirely
unavailable or simply severely dispreferred. Crucially, our data does
attest local readings, albeit that they are not preferred across the
board but preferred, as it seems, only by a small, but substantial
number of consistent localists.

>>>>

These two varieties of grammaticalism give rise to different
predictions about preferred readings. The preference for readings that
weak grammaticalism predicts mirrors the entailment relations in
(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
\as-sentences weak grammaticalism predicts that local readings are
preferred over global readings which in turn are preferred over
literal readings; for \es-sentences weak grammaticalism predicts that
global readings are most preferred, while literal and local readings
are not ranked with respect to preference. Strong grammaticalism, on
the other hand, predicts that \as-sentences preferably get either a
local or a global reading rather than a literal reading, but does not
rank these former two with respect to each other because they differ
in more than one application of the $\exh(\cdot)$ operator. For
\es-sentences, then, strong grammaticalism does not predict \emph{any}
preference relations between candidate readings at all.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lcc}
    & \multicolumn{2}{c}{preference \& availability}
    \\ \cmidrule(r){2-3}
    theoretical position
    & \as
    & \es
    \\ \midrule
    traditionalism
    \\
    \ \ weak restricted 
    & \lit > \glb 
    & \lit > \glb
    \\
    \ \ weak unrestricted
    & \lit > \glb > \loc 
    & \lit > \glb
    \\
    \ \ strong restricted
    & \glb > \lit 
    & \glb > \lit
    \\
    \ \ strong unrestricted
    & \glb > \loc > \lit 
    & \glb > \lit
    \\
    conventionalism
    \\
    \ \ defaultism
    & \loc >  \lit 
    & \loc >  \lit
    \\
    \ \ literalism
    & \lit >  \loc 
    & \lit >  \loc
    \\
    grammaticalism
    \\
    \ \ weak
    & \loc > \glb > \lit 
    & \glb > \lit, \loc
    \\
    \ \ strong
    & \glb, \loc > \lit 
    & \glb, \loc , \lit
    \\
  \end{tabular}
  \caption{Predictions of the relevant theoretical positions. Listed
    are the predicted preference relations. If a reading is not
    listed, it is predicted to be unavailable.}
  \label{tab:predictions}
\end{table}

@@

High scores of success in our general control condition clearly
indicate that participants understood the incremental verification
task and were in general able to give judgements at the earliest
possible point in a picture sequence. Results obtained for the
preference-related controls moreover show that our design is able to
detect multiple readings and preferences among these. Crucially, the
amount of response types for \lc- and \ec-readings reflected the known
preference for the former, \emph{irrespective} of the order in which
each reading could first be judged in a given sequence. Given this,
the best and most straightforward explanation of the observed data is
the hypothesis that the actual preferences among readings for both
\as- and \es-sentences alike are:
\begin{exe}
  \ex \label{bsp:observed-preferences} \lit \ > \ \loc \ \ ( > \glb)
\end{exe}
where it is unclear whether the global readings are entirely
unavailable or simply severely dispreferred. Crucially, our data does
attest local readings, albeit that they are not preferred across the
board but preferred, as it seems, only by a small, but substantial
number of consistent localists.

This is bad news for both traditionalism and grammaticalism, as no
version of either would predict the pattern in
(\ref{bsp:observed-preferences}). The main problem is that
traditionalism, if left on its own, fails to predict local readings,
while grammaticalism, when it relies on the strongest meaning
hypothesis, fails to predict the preference order altogether. What are
the problems exactly? Could either position be aided by innocuous
auxiliary assumptions to be compatible with
(\ref{bsp:observed-preferences})?

It is not a major obstacle for traditionalism to predict that global
readings are available. The weak variety of traditionalism holds that
the extra assumptions needed to derive global readings are not
standardly available, and so traditionalism is compatible with a lack
of observed global readings. Alternatively, traditionalists could
argue that the task's rather high processing demands lead to a
suppression of global implicature readings, in line with the findings
of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. Unfortunately, to the extent that global
readings are explained away, traditionalism also looses the
possibility of accounting for local readings of \as-sentences in its
unrestricted variety.\fn{Remember that what we called unrestricted
  traditionalism can account for local readings of \as-sentences by
  assuming that a sentence of the form \emph{Some of the $X$ are
    related to some of the $Y$} is a feasible alternative.} This is
because unrestricted traditionalism explains local and global readings
of \as-sentences in essentially the same manner. On top of that,
traditionalism cannot explain local readings for \es-sentences at
all. In sum, traditionalism alone cannot explain
(\ref{bsp:observed-preferences}), but needs an additional explanation
of local readings for \emph{both} \as- \emph{and} \es-sentences.

Grammaticalism, on the other hand, fails to predict the preference
relation in (\ref{bsp:observed-preferences}), because these strictly
contradict the strongest meaning hypothesis in either of its suggested
varieties.

\bigskip
